---
title: "SPE_EDU_formal_analysis"
author: "HelenLiu"
output: html_document
---
## This script is used to perform ramdom effect model of effect size, sensitivity analysis, test for publication bias and subgroup analysis ##

```{r import pakage}
library(tidyverse)
library(metafor)
library(meta)
#install.packages("extrafont") #set fronts in times 
library(extrafont)
```

## import df

```{r import df}
#set working directory
cur <- getwd()
setwd(cur)

#import csv
effect_size <- read.csv("../datasheets/effect_size.csv")
head(effect_size)
```

## prepare dataframe

```{r}
df <- effect_size %>%
  dplyr::select(
    id,
    Information,
    N,
    ES,
    VI,
    "Cohort"   = subgroup1,
    "Context"   = subgroup2,
    "Materials"  = subgroup3,
    "Valence" = subgroup4
  ) %>%
  dplyr::filter(row_number() %in% c(1:20))
  
df1 <- escalc(measure="SMD",  data=df, yi= ES, vi = VI,  slab=paste("Study ID:", id))#transfer into escalc format
view(df1)
#reroder
df1 <- df1[order(df1$ES), ]
```

## combined effect size summary

```{r metafor combine effect size}
### fit random-effects model
res <- rma(yi,
           vi,
           data = df1,
           )
res
#I^2=80.29%%,REM

# Prediction interval for primary effect size
predict_primary <- predict(res)
predict_primary
```

## forest plot overall 

```{r metafor combine effect size}
# funtion to add  labs in forset plot
mlabfun <- function(text, res) {
  list(bquote(paste(
    .(text),
    " (Q = ",
    .(formatC(
      res$QE, digits = 2, format = "f"
    )),
    ", df = ",
    .(res$k - res$p),
    ", p ",
    .(metafor:::.pval(
      res$QEp,
      digits = 2,
      showeq = TRUE,
      sep = " "
    )),
    ", ",
    I ^ 2,
    " = ",
    .(formatC(
      res$I2, digits = 1, format = "f"
    )),
    "%) "
    #tau^2, " = ", .(formatC(res$tau2, digits=2, format="f")), ")"
  )))
}
###

tiff(file="forest_overall.tiff",
     res=800,width = 9000,height = 4800)#save tiff

forest(
  res,
  #fonts = "times",
  slab = paste(
    df1$Information
  ),
  header="Author(s) and Year", mlab = mlabfun("RE Model for All Studies", res)
    #   "RE Model for All Studies: Q(19) = 81.29, p = 0.00, I^2 = 80.29%"
) 
dev.off() 
#save graph 
```

## confirm the results with meta package

```{r meta combine effect size，forest}
#devtools::install_github("MathiasHarrer/dmetar")
library(meta)
res1 <- metagen(TE = ES, seTE = sqrt(VI),
                data = df1,
                studlab = df1$Information,
                fixed = FALSE,
                random = TRUE, 
                #method.tau = "SJ", hakn = TRUE,  
                prediction = TRUE, sm = "SMD")
res1

#forest(res1,
       #fonts = "Times New Roman",
       #slab = paste(
      #df1$Information
  #),
  #header="Author(s) and Year")
```

##Influence analysis in meta-analysis using leave-one-out method

```{r sensitivity analysis}
#font_import() #import fronts
#element_text(family="Times New Roman") #import fronts 
#loadfonts()       #Register fonts for Windows bitmap output

#fonts() 

#sensitivity analysis forest plot
metainf(res1)

tiff(file="forest_sensitivity.tiff",
     res=800,width = 9000,height = 4800)#save tiff
forest(metainf(res1),
       #fonts = "times",
       )
dev.off()

#### addtional analysis
library(dmetar)
InA <- InfluenceAnalysis(x = res1, random = TRUE) 
plot(InA)
plot(InA, "influence") #输出 influence 图 plot(InA, "Baujat") #Baujat 图

plot(InA, "I2") #输出按 I^2 排序的图 plot(inf.analysis, "es") #输出按 Effect size 排序的图
plot(InA, "es")
```

## publication bias, funnel plots 
 
```{r publication bias }
#funnel plot
tiff(file="funnel.tiff",
     res=800,width = 7600,height = 4800)#put infront of code
funnel(res1, 
       fonts = "times",
       xlab = "Hedges' g")
dev.off()

#trimfill funnel plot
# corrected effect size
res2 <- trimfill(res1)
res2
funnel(res2, xlab = "Hedges' g")
##

#contour-enhanced funnel plot
tiff(file="funnel_contour-enhanced.tiff",
     res=800,width = 7000,height = 4800)#save tiff

funnel(
  res2,
  xlab = "Hedges' g",
  xlim = c(-1.5,1.5),
  #contour = c(.9,.95,.99),
  contour = c(.95, .975, .99),
  col.contour = c("darkblue", "blue", "lightblue")
) 
legend(
  0.8,
  0,
  c("p>0.05", "0.025<p<0.05", "0.01<p<0.025", "0<p<0.01"),
  bty = "n",
  fill = c("white", "darkblue", "blue", "lightblue")
) 

dev.off()
  
#Egger's test
library(dmetar) 
eggers.test(x = res1)
```

## subgroup analysis

```{r meta subgroup analsysis}
###cohort 
dfx <- df1 %>% dplyr::filter(id != 6) # filter students at high school level(n =1)
View(dfx)
res_cohort <- metagen(TE = ES, seTE = sqrt(VI),
                data = dfx,
                studlab = dfx$information,
                fixed = FALSE,
                random = TRUE, 
                method.tau = "SJ", hakn = TRUE,  
                prediction = TRUE, sm = "SMD")
res_cohort
cohort.subgroup <- update.meta(res_cohort,  
        subgroup = Cohort,  
        random = TRUE,  
        fixed = FALSE) 
cohort.subgroup

####research  context 
context.subgroup <- update.meta(res1,  
        subgroup = Context,  
        random = TRUE,  
        fixed = FALSE) 
context.subgroup

###valence of materials
valence.subgroup <- update.meta(res1,  
        subgroup = Valence,  
        random = TRUE,  
        fixed = FALSE) 
valence.subgroup 

##Form of learning materials
dfj <- df1 %>% dplyr::filter(id != 2 & id != 3) #filter na study 
View(dfj)
res_materials <- metagen(TE = ES, seTE = sqrt(VI),
                data = dfj,
                studlab = dfj$information,
                fixed = FALSE,
                random = TRUE, 
                method.tau = "SJ", hakn = TRUE,  
                prediction = TRUE, sm = "SMD")
res_materials

material.subgroup <- update.meta(res_materials,  
        subgroup = Materials,  
        random = TRUE,  
        fixed = FALSE) 
material.subgroup 
```

